NTM CT Scoring - Initial Agreement

### 2023-05-18 Stacey Martiniano/ntm_agreement.qmd
last report with kappas for everything

    select(feature, location, A:C) %>%
    pivot_longer(A:C) %>%

@@

      select(location, A:C) %>%
      pivot_longer(A:C) %>%

@@

```{r}
# Gold standard data
dup_df = data %>% 
  arrange(scan_id, scorer) %>%
  filter(scan_id %in% dups$original_ssid) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  ungroup()
# Function
compare = function(df,scan_num){
  df = df %>% filter(scan_id == scan_num) %>%
    group_by(scorer,scan_id) %>%
    mutate(n = row_number()) %>% ungroup() %>%
    pivot_longer(bronchiectasis_rul:atelectasis___6,
                           names_to = c("feature", "location"),
                           names_pattern = "(.*)_(.*)$"
  ) %>% 
    mutate(
      feature = gsub("__", "", feature),
      feature = str_to_title(gsub("_", " ", feature))
    ) 
  df$location <- factor(df$location,
                        levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", 
                                   "lul", "rll", "rml", "rul"),
                        labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", 
                                   "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
  )
  df$value <- factor(df$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
  # One column per scorer
  df <- df %>% 
    pivot_wider(names_from = scorer, values_from = value) %>%
    pivot_wider(names_from = n, values_from = A:C) %>%
    arrange(feature,location)
  # Kappa for the whole scan
  af = kappa2(df[,c("A_1","A_2")])
  dl = kappa2(df[,c("B_1","B_2")])
  jw = kappa2(df[,c("C_1","C_2")])
  cat("\n")
  cat("### Overall")
  cat("\n")
  p = df %>%
    select(feature, location, A_1:C_2) %>%
    pivot_longer(A_1:C_2) %>%
    ggplot(., aes(x = name, y = location, fill = value)) +
    geom_tile(color = "black") +
    theme_bw() +
    labs(fill = "", x = "Scorer", y = "Location") +
    custom_colors +
    facet_wrap(~feature)
  cat("\n")
  print(p)
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for A"," was ",round(af$value,3)," (p = ",
      format.pval(af$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for B"," was ",round(dl$value,3)," (p = ",
      format.pval(dl$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for C"," was ",round(jw$value,3)," (p = ",
      format.pval(jw$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  # Analyze by feature
  cat("\n")
  cat("### By Feature and Scorer")
  cat("\n")
  invisible(lapply(levels(factor(df$feature)), function(f){
    t = data.frame(df[df$feature == f,c("A_1","A_2","B_1","B_2","C_1","C_2")])
    rownames(t) = as.character(df$location[df$feature == f])
    af = kappa2(t[,c("A_1","A_2")])
    dl = kappa2(t[,c("B_1","B_2")])
    jw = kappa2(t[,c("C_1","C_2")])
    p = df %>%
      filter(feature == f) %>%
      select(location, A_1:C_2) %>%
      pivot_longer(A_1:C_2) %>%
      ggplot(., aes(x = name, y = location, fill = value)) +
      geom_tile(color = "black") +
      theme_bw() +
      labs(fill = "", x = "Scorer", y = "Location") +
      custom_colors
    cat("\n")
    cat("\n")
    cat("####",f)
    cat("\n")
    cat("\n")
    print(p)
    cat("\n")
    cat("\n")
    if(is.nan(af$value)){
      cat("\n")
      cat("Agreement within A",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for A",f," was ",round(af$value,3)," (p = ",
          format.pval(af$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
    if(is.nan(dl$value)){
      cat("\n")
      cat("Agreement within B",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for B",f," was ",round(dl$value,3)," (p = ",
          format.pval(dl$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
    if(is.nan(jw$value)){
      cat("\n")
      cat("Agreement within C in",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for C",f," was ",round(jw$value,3)," (p = ",
          format.pval(jw$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
  }))
}
```

>>>>

    select(feature, location, A:GS) %>%
    pivot_longer(A:GS) %>%

@@

      select(location, A:GS) %>%
      pivot_longer(A:GS) %>%

@@

```{r}
# Gold standard data
dup_df = data %>% 
  arrange(scan_id, scorer) %>%
  filter(scan_id %in% dups$original_ssid) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  ungroup()
# Function
compare = function(df,scan_num){
  df = df %>% filter(scan_id == scan_num) %>%
    group_by(scorer,scan_id) %>%
    mutate(n = row_number()) %>% ungroup() %>%
    pivot_longer(bronchiectasis_rul:atelectasis___6,
                           names_to = c("feature", "location"),
                           names_pattern = "(.*)_(.*)$"
  ) %>% 
    mutate(
      feature = gsub("__", "", feature),
      feature = str_to_title(gsub("_", " ", feature))
    ) 
  df$location <- factor(df$location,
                        levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", 
                                   "lul", "rll", "rml", "rul"),
                        labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", 
                                   "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
  )
  df$value <- factor(df$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
  # One column per scorer
  df <- df %>% 
    pivot_wider(names_from = scorer, values_from = value) %>%
    pivot_wider(names_from = n, values_from = A:C) %>%
    arrange(feature,location)
  # Kappa for the whole scan
  af = kappa2(df[,c("A_1","A_2")])
  dl = kappa2(df[,c("B_1","B_2")])
  jw = kappa2(df[,c("C_1","C_2")])
  cat("\n")
  cat("### Overall")
  cat("\n")
  p = df %>%
    select(feature, location, A_1:C_2) %>%
    pivot_longer(A_1:C_2) %>%
    ggplot(., aes(x = name, y = location, fill = value)) +
    geom_tile(color = "black") +
    theme_bw() +
    labs(fill = "", x = "Scorer", y = "Location") +
    custom_colors +
    facet_wrap(~feature)
  cat("\n")
  print(p)
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for A"," was ",round(af$value,3)," (p = ",
      format.pval(af$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for B"," was ",round(dl$value,3)," (p = ",
      format.pval(dl$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for C"," was ",round(jw$value,3)," (p = ",
      format.pval(jw$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  # Analyze by feature
  cat("\n")
  cat("### By Feature and Scorer")
  cat("\n")
  invisible(lapply(levels(factor(df$feature)), function(f){
    t = data.frame(df[df$feature == f,c("A_1","A_2","B_1","B_2","C_1","C_2")])
    rownames(t) = as.character(df$location[df$feature == f])
    af = kappa2(t[,c("A_1","A_2")])
    dl = kappa2(t[,c("B_1","B_2")])
    jw = kappa2(t[,c("C_1","C_2")])
    p = df %>%
      filter(feature == f) %>%
      select(location, A_1:C_2) %>%
      pivot_longer(A_1:C_2) %>%
      ggplot(., aes(x = name, y = location, fill = value)) +
      geom_tile(color = "black") +
      theme_bw() +
      labs(fill = "", x = "Scorer", y = "Location") +
      custom_colors
    cat("\n")
    cat("\n")
    cat("####",f)
    cat("\n")
    cat("\n")
    print(p)
    cat("\n")
    cat("\n")
    if(is.nan(af$value)){
      cat("\n")
      cat("Agreement within A ",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for A ",f," was ",round(af$value,3)," (p = ",
          format.pval(af$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
    if(is.nan(dl$value)){
      cat("\n")
      cat("Agreement within B ",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for B ",f," was ",round(dl$value,3)," (p = ",
          format.pval(dl$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
    if(is.nan(jw$value)){
      cat("\n")
      cat("Agreement within C in",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for C ",f," was ",round(jw$value,3)," (p = ",
          format.pval(jw$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
  }))
}
```
